parameters

### 2020-01-15 manuscript/manuscript.Rmd
parameter table

The ASReview software knows the following parameters: 
```{r}
# configurations table 
tab <- lapply(params, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("configurations")

@@

kable(tab, format  = "pandoc")
```

\
This leads to  `r nrow(combins)` combinations of configurations:

>>>>

```{r}
# configurations table 
tab <- lapply(params, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("configurations")

@@

```

ASReview takes the following parameters/arguments:

- a model
- a query strategy
- a balance strategy
- feature extraction

```{r}
kable(tab, format  = "pandoc")
```

This leads to  `r nrow(combins)` combinations of configurations:
